Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-17 journal paper/content/sec-theory.tex
Fixed a reference.
Minor edits.

An algorithm is called \emph{\bmonotone} if it can only get better over time: $\rew_i(\cdot)$ is non-decreasing (and therefore $\BIR(\cdot)$ is non-decreasing). We argue this is a mild assumption, see
Appendix~\ref{app:MAB-mono}.

@@

\xhdr{Time-discounted utility.}
Corollary~\ref{cor:DG-dominance} holds under a more general model which allows time-discounting: namely, the utility of each principal $i$ in each global round $t$ is $U_{i,t}(r_t)$ if this principal is chosen, and $0$ otherwise, where $U_{i,t}(\cdot)$ is an arbitrary non-decreasing function with $U_{i,t}(0)>0$.

@@

\noindent Weak BIR-dominance can be redefined similarly.
Theorem~\ref{thm:random-clean} and Theorem~\ref{thm:SoftMax-weak} extend to these generalized versions; the easy modifications are omitted.

>>>>

An algorithm is called \emph{\bmonotone} if it can only get better over time: $\rew_i(\cdot)$ is non-decreasing (and therefore $\BIR(\cdot)$ is non-decreasing). We argue this is a mild assumption, see
Appendix~\ref{app:examples}.

@@

\xhdr{Time-discounted utility.}
Theorem~\ref{thm:DG-dominance} and Corollary~\ref{cor:DG-dominance} holds under a more general model which allows time-discounting: namely, the utility of each principal $i$ in each global round $t$ is $U_{i,t}(r_t)$ if this principal is chosen, and $0$ otherwise, where $U_{i,t}(\cdot)$ is an arbitrary non-decreasing function with $U_{i,t}(0)>0$.

@@

\noindent Weak BIR-dominance can be redefined similarly.
Theorem~\ref{thm:random-clean} and~\ref{thm:SoftMax-weak} easily extend to these versions.
